Verifying Demonstrations

### 2019-06-28 paper/DB-anon-cred.tex
Adds arguments for DB-Schnorr similar to Schnorr (for proof)

\subsection{Security analysis}

>>>>

\subsection{\Acl*{ZK} and \acl*{PK}}

The main difference between this protocol and the Schnorr protocol is that we 
have the prover compute responses for \(k\) different challenges, \(c_1, 
  \dotsc, c_k\).
However, in the authentication step, the verifier chooses only one of those 
challenges.
From the simulator's (and extractor's) perspective, there is no difference 
whether the verifier first chooses \(k\) and then chooses one of those \(k\) 
challenges, or if the verfifier chooses the one challenge directly;
the distribution is the same, \(\frac{k}{n}\times \frac{1}{k} = \frac{1}{n}\).
Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
protocol with soundness error \(2^{-kn}\) still 
holds~\cite[\eg][]{OnSigmaProtocols}.

\subsection{\acs*{DBMF}, \acs*{DBDH} and \acs*{DBTF} resistance}
